### 2016-03-27 chapters/concept.tex
contributions fixed, workflow image added, citation added
xml coloring added
minor visual changes

[Diagram showing the general workflow]

%TODO: Abstrakte Beschreibung des Nutzer-Szenarios

%TODO: Schaubild
unstructured product line $\rightarrow$ generated feature model $\rightarrow$ optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert $\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire $\Rightarrow$ Product (variant)\\

@@

@@

We also introduce a data structure to hold the definition of a questionnaire. To archive easy integration we decided for a definition in XML. We defined the necessary tags to create a questionnaire which are displayed in the following code snippet:

\begin{figure}
\begin{lstlisting}
<configurationSurvey>
	<projectName>Name</projectName>
	<section id="0">
		<name>Section Name</name>
		<description>Section description</description>
	</section>
	<page id="0" sectionId="0">
		<question>Question for the user</question>
		<answers type="alternative">
			<answer nextPageId="1">
				<label>Answer label</label>
				<description>
					Answer description
				</description>
				<dependencies>
					<feature selection="false">
						Unselected feature
					</feature>
					<feature>selected feature</feature>
				</dependencies>
			</answer>
		</answers>
	</page>
</configurationSurvey>
\end{lstlisting}
\caption{Examplary XML file for a  questionnaire}
\end{figure}

\begin{tabulary}{\linewidth}{LLL}
\textbf{Tag} & \textbf{attributes} & \textbf{child tags}\\
\hline
configurationSurvey & & projectName, section, page\\
section & id & name, description\\
page & id, sectionId & question, answers\\
answers & type & answer\\
answer & nextPageId & label, description, dependencies\\
dependencies & & feature\\
feature & selection & \\
\end{tabulary}\vspace{2.5em}

The individual tags are explained as follows:

\begin{itemize}
\item \texttt{configurationSurvey}: The root tag to contain all other tags for the questionnaire.
\item \texttt{section}: Enables grouping of question-pages. Also displays the name and description at the top of every page.
\item \texttt{page}: Contains a question and the corresponding answers. Also has an indicator for a section
\item \texttt{answers}: Contains the individual possible answers and groups them in the specified manner.
\item \texttt{answer}: Defines the displayed text of an answer as well as the corresponding features. Can also have an indicator for the next page.
\item \texttt{dependencies}: Defines the (un-)selection of features, if the corresponding answer gets selected.
\end{itemize}

>>>>

%unstructured product line $\rightarrow$ generated feature model $\rightarrow$ %optimizing (via SAT-solver?) $\rightarrow$ domain knowledge of an expert %$\Rightarrow$ Questionnaire $\rightarrow$ Feature model + Questionnaire %$\Rightarrow$ Product (variant)\\

@@

\begin{figure}[H]
	\includegraphics{img/img-workflow.pdf}
	\caption{Diagram showing the general workflow}
	\label{img-workflow}
\end{figure}

@@

We also introduce a data structure to hold the definition of a questionnaire. To archive easy integration we decided for a definition in XML. We defined the necessary tags to create a questionnaire which are displayed in figure~\ref{fig:xmlFigure}.

\begin{figure}[H]
\begin{tabulary}{\linewidth}{LLL}
\textbf{Tag} & \textbf{attributes} & \textbf{child tags}\\
\hline
configurationSurvey & & projectName, section, page\\
section & id & name, description\\
page & id, sectionId & question, answers\\
answers & type & answer\\
answer & nextPageId & label, description, dependencies\\
dependencies & & feature\\
feature & selection & \\
\end{tabulary}\vspace{2.5em}
\end{figure}

The individual tags are explained as follows:
\begin{itemize}
\item \texttt{configurationSurvey}: The root tag to contain all other tags for the questionnaire.
\item \texttt{section}: Enables grouping of question-pages. Also displays the name and description at the top of every page.
\item \texttt{page}: Contains a question and the corresponding answers. Also has an indicator for a section
\item \texttt{answers}: Contains the individual possible answers and groups them in the specified manner.
\item \texttt{answer}: Defines the displayed text of an answer as well as the corresponding features. Can also have an indicator for the next page.
\item \texttt{dependencies}: Defines the (un-)selection of features, if the corresponding answer gets selected.
\end{itemize}

\begin{figure}[H]
	\lstset{language=XML}
	\begin{lstlisting}
	<configurationSurvey>
		<projectName>Name</projectName>
		<section id="0">
			<name>Section Name</name>
			<description>Section description</description>
		</section>
		<page id="0" sectionId="0">
			<question>Question for the user</question>
			<answers type="alternative">
				<answer nextPageId="1">
					<label>Answer label</label>
					<description>
						Answer description
					</description>
					<dependencies>
						<feature selection="false">
							Unselected feature
						</feature>
						<feature>selected feature</feature>
					</dependencies>
				</answer>
			</answers>
		</page>
	</configurationSurvey>
	\end{lstlisting}
	\caption{Examplary XML file for a  questionnaire}
	\label{fig:xmlFigure}
\end{figure}
